Exploring probability distributions for bivariate temporal granularities

### 2019-12-09 main.Rmd
minor changes till cyclic granularities fixed

\begin{equation}
\begin{split}
pseudomonth & = Alter^{12}_{11,-1}(day, \\
  Alter^{12}_{9,-1}(day, \\
  Alter^{12}_{6,-1}(day,  \\
  Alter^{12}_{4,-1)}(day, \\
  Alter^{12}_{(2,-3)}(day, \\
  Group_{31}(day))))))
\end{split}
\end{equation}

where the granularity pseudomonth is generated by grouping 31 days, and then shrink April (4), June (6), September (9) and November (11) by 1 day, and shrink February (2) by 3 days. [@Ning2002-tf]

@@

The authors would like to thank the cohort at [NUMBATS](https://www.monash.edu/news/articles/team-profile-monash-business-analytics-team), Monash University for sharing their wisdom and experience of developing R packages, Dr. Peter Toscas [from Data61 CSIRO](https://data61.csiro.au/) for providing useful inputs for improving the analysis of smart meter application. The package `gravitas` was built under [Google Summer of Code, 2019](https://summerofcode.withgoogle.com/archive/) This article was created with knitr [@knitr] and R Markdown [@rmarkdown]. The project's Github repository <https://github.com/Sayani07/paper-gravitas> contains all required materials required to reproduce this article.

>>>>

\begin{equation*}
\begin{split}
pseudomonth = Alter^{12}_{11,-1}(day, Alter^{12}_{9,-1}(day, \\
  Alter^{12}_{6,-1}(day, Alter^{12}_{4,-1)}(day, \\
  Alter^{12}_{(2,-3)}(day, Group_{31}(day))))))
\end{split}
\end{equation*}

, where the granularity pseudomonth is generated by grouping 31 days, and then shrink April (4), June (6), September (9) and November (11) by 1 day, and shrink February (2) by 3 days. [@Ning2002-tf]

@@

The authors would like to thank the cohort at [NUMBATS](https://www.monash.edu/news/articles/team-profile-monash-business-analytics-team), Monash University for sharing their wisdom and experience of developing R packages, Dr. Peter Toscas [from Data61 CSIRO](https://data61.csiro.au/) for providing useful inputs for improving the analysis of smart meter application. The package `gravitas` was built under [Google Summer of Code, 2019](https://summerofcode.withgoogle.com/archive/). This article was created with knitr [@knitr] and R Markdown [@rmarkdown]. The project's Github repository <https://github.com/Sayani07/paper-gravitas> contains all required materials required to reproduce this article.
